---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

library(oxfordtheme)
library(ggplot2)
```

# oxfordtheme: Oxford Theme and Theme Components

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/OxfordIHTM/oxfordtheme/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/OxfordIHTM/oxfordtheme/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/OxfordIHTM/oxfordtheme/branch/main/graph/badge.svg)](https://app.codecov.io/gh/OxfordIHTM/oxfordtheme?branch=main)
<!-- badges: end -->

Palette, theme, and theme components based on [University of Oxford](https://ox.ac.uk)'s [visual identity guidelines](https://communications.web.ox.ac.uk/communications-resources/visual-identity/identity-guidelines). 

## What does `oxfordtheme` do?

`oxfordtheme` aims to provide templates, themes, and theme components for colour palettes, typography, and layout compliant with [University of Oxford](https://ox.ac.uk)'s [visual identity guidelines](https://communications.web.ox.ac.uk/communications-resources/visual-identity/identity-guidelines).for use in the R language for statistical computing publishing ecosystem.

Currently, the package provides colour palettes consistent with the colours prescribed by the university visual identity guidelines. Additional templates, themes, and theme components will be included over time.

## Installation

`oxfordtheme` is not yet available on [CRAN](https://cran.r-project.org) but can be installed through the [Oxford IHTM R universe](https://oxfordihtm.r-universe.dev) resository as follows:

```R
install.packages(
  "oxfordtheme", 
  repos = c(
    'https://oxfordihtm.r-universe.dev', 
    'https://cloud.r-project.org'
  )
)
```

## Usage

### Oxford colours

Based on the [University of Oxford](https://ox.ac.uk)'s [visual identity guidelines](https://communications.web.ox.ac.uk/communications-resources/visual-identity/identity-guidelines), the following colours are available from this package:

```{r oxford-colours, echo = FALSE}
oxford_colours |>
  knitr::kable()
```

### Oxford palettes

Based on the [University of Oxford](https://ox.ac.uk)'s [visual identity guidelines](https://communications.web.ox.ac.uk/communications-resources/visual-identity/identity-guidelines) and the carefully curated colour groups of the official University [theme packs](https://communications.web.ox.ac.uk/communications-resources/visual-identity/identity-guidelines/theme-packs), the following palettes are available from this package:

#### Heritage

```{r oxford-palettes-heritage-code}
oxford_theme_palettes()$heritage
```

```{r oxford-palettes-heritage-show, echo = FALSE, fig.height = 1}
structure(oxford_theme_palettes()$heritage, class = "palette", name = "heritage")
```

#### Contemporary

```{r oxford-palettes-contemporary-code}
oxford_theme_palettes()$contemporary
```

```{r oxford-palettes-contemporary-show, echo = FALSE, fig.height = 1}
structure(oxford_theme_palettes()$contemporary, class = "palette", name = "contemporary")
```

#### Celebratory

```{r oxford-palettes-celebratory-code}
oxford_theme_palettes()$celebratory
```

```{r oxford-palettes-celebratory-show, echo = FALSE, fig.height = 1}
structure(oxford_theme_palettes()$celebratory, class = "palette", name = "celebratory")
```

#### Corporate

```{r oxford-palettes-corporate-code}
oxford_theme_palettes()$corporate
```

```{r oxford-palettes-corporate-show, echo = FALSE, fig.height = 1}
structure(oxford_theme_palettes()$corporate, class = "palette", name = "corporate")
```


## Community guidelines

Feedback, bug reports and feature requests are welcome; file issues or seek support [here](https://github.com/OxfordIHTM/oxfordtheme/issues). If you would like to contribute to the package, please see our [contributing guidelines](https://oxford-ihtm.io/oxfordtheme/CONTRIBUTING.html).

This project is released with a [Contributor Code of Conduct](https://oxford-ihtm.io/oxfordtheme/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
