---
title: "Oxford forestploter Themes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Oxford forestploter Themes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "ragg_png"
)
```

```{r setup, echo = FALSE, message = FALSE}
library(oxthema)
library(forestploter)
library(grid)
library(showtext)
library(sysfonts)

font_add_google("Roboto")
font_add_google("Marcellus")
font_add_google("Montserrat")
font_add_google("Noto Serif Display")
font_add_google("Bebas Neue")
font_add_google("Phudu", db_cache = FALSE)
```

## Oxford theme for `forestploter` package

Using the example data in the `forestploter` and processing it in the same way as show in the `forestploter` README as per code below:

```{r fp-data, echo = TRUE}
# Read and process example data from forestploter package

## Read example data from forestploter package
dt <- read.csv(
  system.file("extdata", "example_data.csv", package = "forestploter")
)

## Indent the subgroup if there is a number in the placebo column
dt$Subgroup <- ifelse(
  is.na(dt$Placebo), dt$Subgroup, paste0("   ", dt$Subgroup)
)

## NA to blank
dt$Treatment <- ifelse(is.na(dt$Treatment), "", dt$Treatment)
dt$Placebo   <- ifelse(is.na(dt$Placebo), "", dt$Placebo)
dt$se        <- (log(dt$hi) - log(dt$est)) / 1.96

## Add a blank column for the forest plot to display CI.
## Adjust the column width with space. 
dt$` ` <- paste(rep(" ", 20), collapse = " ")

## Create confidence interval column to display
dt$`HR (95% CI)` <- ifelse(
  is.na(dt$se), "",
  sprintf("%.2f (%.2f to %.2f)", dt$est, dt$low, dt$hi)
)
```

we demonstrate how to use the based `theme_oxford_forest()` to provide a custom theme to a `forestploter` forest plot as follows:

```{r fp-theme, eval = FALSE}
# Create forest plot from dt and then apply theme_oxford_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Roboto plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford royal blue",
            theme = theme_oxford_forest())

## Print plot
plot(p)
```


```{r fp-theme-show, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 7, fig.showtext = TRUE, fig.retina = 1}
# enable showtext
showtext_auto()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Roboto plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford royal blue",
            theme = theme_oxford_forest())

# Print plot
plot(p)
```

### Using Oxford heritage forest plot theme

Using the same example data, we use the `theme_heritage_forest()` to theme the output forest plot as follows:

```{r fp-heritage, eval = FALSE}
# Create forest plot from dt and then apply theme_heritage_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Marcellus plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford green",
            theme = theme_heritage_forest())

## Print plot
plot(p)
```


```{r fp-heritage-show, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 7, fig.showtext = TRUE, fig.retina = 1}
# enable showtext
showtext_auto()

p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Marcellus plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford green",
            theme = theme_heritage_forest())

# Print plot
plot(p)
```


### Using Oxford contemporary forest plot theme

Using the same example data, we use the `theme_contemporary_forest()` to theme the output forest plot as follows:

```{r fp-contemporary, eval = FALSE}
# Create forest plot from dt and then apply theme_contemporary_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Montserrat plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford aqua",
            theme = theme_contemporary_forest())

## Print plot
plot(p)
```


```{r fp-contemporary-show, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 7, fig.showtext = TRUE, fig.retina = 1}
# enable showtext
showtext_auto()

p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Montserrat plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford aqua",
            theme = theme_contemporary_forest())

# Print plot
plot(p)
```


### Using Oxford celebratory forest plot theme

Using the same example data, we use the `theme_celebratory_forest()` to theme the output forest plot as follows:

```{r fp-celebratory, eval = FALSE}
# Create forest plot from dt and then apply theme_celebratory_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Noto Serif Display plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford viridian",
            theme = theme_celebratory_forest())

## Print plot
plot(p)
```


```{r fp-celebratory-show, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 7, fig.showtext = TRUE, fig.retina = 1}
# enable showtext
showtext_auto()

# Create forest plot from dt and then apply theme_celebratory_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Noto Serif Display plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford viridian",
            theme = theme_celebratory_forest())

# Print plot
plot(p)
```


### Using Oxford corporate forest plot theme

Using the same example data, we use the `theme_corporate_forest()` to theme the output forest plot as follows:

```{r fp-corporate, eval = FALSE}
# Create forest plot from dt and then apply theme_corporate_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Bebas Neue plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford royal blue",
            theme = theme_corporate_forest())

## Print plot
plot(p)
```


```{r fp-corporate-show, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 7, fig.showtext = TRUE, fig.retina = 1}
# enable showtext
showtext_auto()

# Create forest plot from dt and then apply theme_corporate_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Bebas Neue plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford royal blue",
            theme = theme_corporate_forest())

# Print plot
plot(p)
```


### Using Oxford innovative forest plot theme

Using the same example data, we use the `theme_innovative_forest()` to theme the output forest plot as follows:

```{r fp-innovative, eval = FALSE}
# Create forest plot from dt and then apply theme_innovative_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Phudu plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford viridian",
            theme = theme_innovative_forest())

## Print plot
plot(p)
```


```{r fp-innovative-show, echo = FALSE, fig.align = "center", fig.width = 8, fig.height = 7, fig.showtext = TRUE, fig.retina = 1}
# enable showtext
showtext_auto()

# Create forest plot from dt and then apply theme_innovative_forest()

## Create forest plot
p <- forest(dt[ , c(1:3, 20:21)],
            est = dt$est,
            lower = dt$low, 
            upper = dt$hi,
            sizes = dt$se,
            ci_column = 4,
            ref_line = 1,
            arrow_lab = c("Placebo Better", "Treatment Better"),
            xlim = c(0, 4),
            ticks_at = c(0.5, 1, 2, 3),
            title = "Title in Phudu plain font in Oxford blue",
            footnote = "Footnote in Roboto plain font\nin Oxford viridian",
            theme = theme_innovative_forest())

# Print plot
plot(p)
```
