---
title: "Oxford Theme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Oxford Theme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(oxthema)
library(ggplot2)
```

The `oxthema`  package has a generic/base `ggplot2` theme which is the template from which all other themes in the `oxthema` package is built on. This theme is inspired by Bob Rudis' [hrbrthemes](https://github.com/hrbrmstr/hrbrthemes) package drawing heavily on its typography-centric focus. This function uses the *Roboto* Google font which is the core Oxford san serif font. It is freely downloadable and easily installed on any system.

## Oxford theme palettes for use in plotting

The University of Oxford recommended theme palettes can be used for plotting. Below is code examples of how this can be done with `ggplot2`.

### Bar plot

```{r mtcars-barplot, echo = FALSE, fig.align = "center", fig.height = 6, fig.width = 5}
## Barplot of cyl and vs of mtcars dataset using heritage Oxford theme

### ggplot2
ggplot(
  data = mtcars, 
  mapping = aes(
      x = factor(vs, levels = c(0, 1), labels = c("v-shaped", "straight")), 
      fill = factor(cyl)
    )  
  ) +
  geom_bar() +
  scale_fill_manual(name = "Cylinders", values = oxford_theme_palettes()$heritage) +
  labs(
    title = "This title is in Oxford Blue",
    subtitle = "This subtitle is in Oxford ash grey",
    x = "Engine shape",
    y = "Counts"
  ) +
  theme_oxford(grid = "Y")
```

### Scatter plot

```{r mtcars-scatterplot, echo = FALSE, fig.align = "center", fig.height = 6, fig.width = 5}
## Scatterplot of mpg and disp of mtcars dataset using celebratory Oxford theme

### ggplot2
ggplot(data = mtcars, mapping = aes(x = mpg, y = disp, colour = factor(cyl))) +
  geom_point(size = 5) +
  scale_colour_manual(
    name = "Cylinders", 
    values = oxford_theme_palettes()$celebratory
  ) +
  labs(
    title = "This title is in Oxford Blue",
    subtitle = "This subtitle is in Oxford Ash Grey"
  ) +
  theme_oxford(grid = "XY")
```

### Plotting maps using Oxford palettes

#### Sequential palette

```{r oxford-palette-sequential1, echo = FALSE, fig.align = "center", fig.height = 6, fig.width = 8}
## Plot acute malnutrition using Oxford sequential palette

### Yellow-Orange-Brown
ggplot(data = nut_survey_map) +
  geom_sf(mapping = aes(fill = muac_mam)) +
  scale_fill_gradientn(
    name = "",
    colours = create_palette_sequential(n = 9, name = "ylorbr")
  ) +
  labs(
    title = "Prevalence of moderate child wasting",
    subtitle = "Sequential Yellow-Orange-Brown Colour Palette"
  ) +
  theme_oxford()
```

```{r oxford-palette-sequential2, echo = FALSE, fig.align = "center", fig.height = 6, fig.width = 8}
## Plot acute malnutrition using Oxford sequential palette

### Yellow-Green-Blue
ggplot(data = nut_survey_map) +
  geom_sf(mapping = aes(fill = muac_sam)) +
  scale_fill_gradientn(
    name = "",
    colours = create_palette_sequential(n = 9, name = "ylgnbu")
  ) +
  labs(
    title = "Prevalence of severe child wasting",
    subtitle = "Sequential Yellow-Green-Blue Colour Palette"
  ) +
  theme_oxford()
```

#### Divergent palette

```{r oxford-palette-divergent1, echo = FALSE, fig.align = "center", fig.height = 6, fig.width = 8}
## Plot period prevalence of fever and diarrhoea using Oxford divergent palette

### Pink-Yellow-Green
ggplot(data = nut_survey_map) +
  geom_sf(mapping = aes(fill = fev)) +
  scale_fill_gradientn(
    name = "",
    colours = create_palette_divergent(n = 11, name = "piylgn")
  ) +
  labs(
    title = "Period prevalence of childhood fever",
    subtitle = "Divergent Pink-Yellow-Green Colour Palette"
  ) +
  theme_oxford()
```

```{r oxford-palette-divergent2, echo = FALSE, fig.align = "center", fig.height = 6, fig.width = 8}
## Plot period prevalence of fever and diarrhoea using Oxford divergent palette

### Purple-Green
ggplot(data = nut_survey_map) +
  geom_sf(mapping = aes(fill = dia)) +
  scale_fill_gradientn(
    name = "",
    colours = create_palette_divergent(n = 11, name = "prgn")
  ) +
  labs(
    title = "Period prevalence of childhood diarrhoea",
    subtitle = "Divergent Purple-Green Colour Palette"
  ) +
  theme_oxford()
```

