---
title: "University of Oxford Colours, Palettes, Fonts, and Themes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{University of Oxford Colours, Palettes, Fonts, and Themes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE}
library(oxthema)
```

Visual identity guidelines serve as a blueprint for maintaining consistency in how an organisation presents itself visually. They emphasise the importance of correctly utilising visual elements to represent the organisation's identity and values. By adhering to these guidelines, uniformity is achieved across all communications, which contributes to fostering a consistent and positive image for the organisation. This unified visual presentation aids in conveying and promoting the organisation's academic excellence and cultural significance effectively. The University of Oxford visual identity guidelines creates such a framework through a set of colours, palettes, fonts, and themes for use in various forms of communication materials and media.

`oxthema` provides utilities for applying the University of Oxford's visual identity and/or branding guidelines. Currently, `oxthema` has colours, palettes, fonts, and themes that is consistent with these guidelines.

* [Oxford colours](https://oxford-ihtm.io/oxthema/articles/oxford-colours.html)

* [Oxford palettes](https://oxford-ihtm.io/oxthema/articles/oxford-palettes.html)

* [Oxford fonts](https://oxford-ihtm.io/oxthema/articles/oxford-fonts.html)

* [Oxford ggplot2 themes](https://oxford-ihtm.io/oxthema/articles/oxford-ggplot2-themes.html)

* [Oxford forestploter themes](https://oxford-ihtm.io/oxthema/articles/oxford-forestploter-themes.html)

